Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-09-01 ms.tex
Started a primer on detector operation.

\title{Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of NIRCam Detectors}

@@

JWST has also been considered for observations of temperate Earth-like planets that orbit their stars at a distance where where water could be in liquid form on their surface.
The TRAPPIST-1 system \citep{gillon2016trappist1Discovery,gillon2017trappist-1sevenp} presents an exciting opportunity to study Earth-sized stars orbiting a 0.1~R$_\odot$ M-type star.
By putting together 10-30 transits, it will be possible to collect enough photons to detect CO$_2$ \citep{barstow2016trappist1habitable,krissansen-totton2018trappist1eJWST} and, optimistically, O$_3$ in the atmosphere of TRAPPIST-1 d with JWST if clouds have a minimal impact to its atmosphere \citep{barstow2016trappist1habitable}.
A critical question in studying planets like TRAPPIST-1 d/e, however, is whether photon-limited performance is possible with JWST observations.

@@

\section{Known Detector Effects}
Known detector effects that could affect stability include:
\begin{itemize}[noitemsep]
	\item \textbf{Intrapixel sensitivity:} - including sub-pixel flat fielding issues and sub-pixel crosshatching on the detectors \citep{shapiro2018crosshatch}
	\item \textbf{Pre-amp reset offsets:} (an Asic-related effect) 
The resets cause discontinuities in the pedestal level of all pixels between frames. This is an effect where averaging over more pixels does not decrease the noise, but reference pixel or background subtraction can. These are discussed in Section \ref{sec:preAmp}.
	\item \textbf{1/f noise:} This is a noise source where most of the noise power is concentrated as low frequencies. 1/f noise causes spatial correlations in the fast-read direction (along detector rows). It is highly correlated between amplifiers, suggesting that it is caused by a common reference voltage. 1/f noise is efficiently removed by reference pixels
	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels. Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector
	\item \textbf{kTC noise:} A random process due to the unknown amount of charge stored at the reset voltage level
\end{itemize}

>>>>

\title{Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors}

@@

JWST has also been considered for observations of temperate Earth-like planets that orbit their stars at a distance where where water could be in liquid form on their surface.
The TRAPPIST-1 system \citep{gillon2016trappist1Discovery,gillon2017trappist-1sevenp} presents an exciting opportunity to study Earth-sized stars orbiting a 0.1~R$_\odot$ M-type star.
By putting together 10-30 transits, it will be possible to collect enough photons to detect CO$_2$ \citep{barstow2016trappist1habitable,krissansen-totton2018trappist1eJWST} and, optimistically, O$_3$ in the atmosphere of TRAPPIST-1 d with JWST if clouds have a minimal impact to its atmosphere \citep{barstow2016trappist1habitable}.
A critical question in studying planets like TRAPPIST-1 d/e, however, is whether photon-limited performance is possible with JWST observations \textcolor{red}{Double Check!}.

@@

\section{A Primer on Detector Operation}
It is helpful to review the basic operation of a NIRCam detector in order to understand the systematics affecting time series.
Figure \ref{fig:npSchematic} shows a schematic of an NP semiconductor junction for a H2RG detector from \citet{smith2008imgPersistence}.
The N-type semiconductor is a negatively-doped HgCdTe crystalline structure that has negative charge carriers (electrons).
The P-type semiconductor is a positively-doped HgCdTe crystalline structure that has positive charge carriers (vacant holes in the lattice structure than can move like electrons).
In reality, the physical size of the P-type semiconductor is much smaller than the N-type and the N-type is responsible for detecting photons.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.6\columnwidth]{smith_np_junction.png}
\caption{A cartoon schematic of a H2RG detector from \citet{smith2008imgPersistence}. }\label{fig:npSchematic}
\end{figure}

The junction of these two materials enables electrons to flow from the N-type material to the P-type material where it can complete a valence shell in the semiconductor material.
This produces a negative charge on the P-type side.
Conversely, the positively charged holes from the P-type material flow to the N-type material to complete the valence shell and this produces a positive charge.
Since there are no charge carriers in the region of electrons in the P-type material and holes in the N-type material, this is called the depletion region.
The positive net charge on the N-type material and negative charge in the P-type material causes a voltage (potential) difference across the detector that can be measured with an amplifier.

Note that Figure \ref{fig:npSchematic} shows the mobile charge carriers only, so the depletion region, with no mobile charges is positively charged on the N-type side and negatively charged on the P-type side.
The undepleted region is electrically neutral because the nuclei of the N-type material have an equal number of extra protons as the negatively charged electrons.
Similarly, the undepleted region of the P-type semiconductor has fewer protons in its atomic nuclei producing an overall neutral charge.
Textbook NP junction schematics sometimes instead show the net charge.

When an incoming photon hits the (check if this is correct) n-type depletion region, it will excite the hole to a higher energy level and this will return it to the P-type side.
A second photon will excite another hole from the N-side that causes it to flow to the P side.
This continues and depletes the size of the depletion region until there is a smaller charge difference across the NP junction.

produce a negatively charged region on the P-type conductor. positive and negative charge carriers to join as completed valence electron shells in the lattice.

\section{Known Detector Effects}

Known detector effects that could affect stability include:
\begin{itemize}[noitemsep]
	\item \textbf{Intrapixel sensitivity:} - including sub-pixel flat fielding issues and sub-pixel crosshatching on the detectors \citep{shapiro2018crosshatch}
	\item \textbf{Pre-amp reset offsets:} (an Asic-related effect) 
The resets cause discontinuities in the pedestal level of all pixels between frames. This is an effect where averaging over more pixels does not decrease the noise, but reference pixel or background subtraction can. These are discussed in Section \ref{sec:preAmp}.
	\item \textbf{1/f noise:} This is a noise source where most of the noise power is concentrated as low frequencies. 1/f noise causes spatial correlations in the fast-read direction (along detector rows). It is highly correlated between amplifiers, suggesting that it is caused by a common reference voltage. 1/f noise is efficiently removed by reference pixels
	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels. Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector
	\item \textbf{kTC noise:} A random process due to the unknown amount of charge stored at the reset voltage level
\end{itemize}
